Modulation and delays in Fourier domain: precessing binaries and LISA-type detector response

### 2016-08-13 docs/paper_method.tex
Changes to accomodate response at high frequencies. Various other changes.
The response at thigh frequencies (for low masses) shows much more structure, including zero-crossings. We now do a resampling of the high-f part to ensure enough points to resolve this structure. The response now also includes the new first order correction to the R-delay.

Other changes:
- EvaluateGABmode now has a tag to include or not the R-delay phase term
- interface for PN extension changed: now tagextpn is a tag to indicate wether to do a PN extension at all, Mfmatch used to indicate wodn to which frequency to u

This rather cumbersome expression is easy to simplify for special cases. For instance, if we expand only the frequency-dependence of $g$ as in~\eqref{eq:expandg}, we obtain
%
\be
	\tilde{s}(f) = \tilde{h}(f) \sum\limits_{r\geq 0} \frac{1}{(2i\pi)^{r}r!} \left( \frac{\partial^{r} }{\partial f^{r}} \frac{\partial^{r} }{\partial t^{r}} g \right)(f,\tf)
\ee
%
which interestingly looks like a Taylor expansion of $g$, but with joint derivatives in frequency and time. Similarly, the expansion~\eqref{eq:expandA} gives
%
\be
	\tilde{s}(f) = \tilde{h}(f) \sum\limits_{q\geq 0} \frac{1}{(2i\pi)^{q}q!} \frac{1}{A} \frac{\ud^{q} A}{\ud f ^{q}}  \left( \frac{\partial^{q} }{\partial t^{q}} g \right)(f,\tf)
\ee
%

@@

>>>>

This rather cumbersome expression is easy to simplify for special cases. For instance, if we expand only the frequency-dependence of $g$ as in~\eqref{eq:expandg}, we obtain
%
\be
	\tilde{s}(f) = \tilde{h}(f) \sum\limits_{r\geq 0} \frac{1}{(2i\pi)^{r}r!} \left( \frac{\partial^{r} }{\partial f^{r}} \frac{\partial^{r} }{\partial t^{r}} g \right)(f,\tf)
\ee
%
which interestingly looks like a Taylor expansion of $g$, but with joint derivatives in frequency and time. Similarly, the expansion~\eqref{eq:expandA} gives
%
\be\label{eq:resultdfA}
	\tilde{s}(f) = \tilde{h}(f) \sum\limits_{q\geq 0} \frac{1}{(2i\pi)^{q}q!} \frac{1}{A} \frac{\ud^{q} A}{\ud f ^{q}}  \left( \frac{\partial^{q} }{\partial t^{q}} g \right)(f,\tf)
\ee
%

@@

\subsubsection{Delays in the LLP approximation for LISA-type detectors}
\label{subsubsec:LISAorbitaldelay}

In the case of a LISA-type detector response, it is interesting to consider the case where the . The following will be mostly relevant for the delay induced by the motion of the constellation around the sun. Indeed, the analysis of the magnitude of the corrections beyond the LLP shows that it is the only one where the figure of merit of the approximation can exceed $10^{-1}$, due to the large baseline of the delay.

If one can neglect the signal related amplitude and phase corrections as given in~\eqref{eq:resultdfA} and~\eqref{eq:resultdffPsiTf}, but one keeps the frequency-dependence in the convolution kernel in~\eqref{}, the general form of the response reads
\begin{equation}
	\tilde{s}(f) = \tilde{h}(f) \int \ud t \, F(t) e^{-2i\pi f d(t)} \int \ud f' \, e^{2i\pi f' (t+d(t) - t_{f})} \,,
\end{equation}
where we recall that we defined $t_{f} \equiv -1/(2\pi)\ud \Psi/\ud f$. If we introduce a new time, defined implicitly by
\be
	\left. (t + d(t) - t_{f})\right|_{t=t_{f}^{d}} = 0 \,,
\ee
The above integral can be formally computed as
\begin{align}
	\tilde{s}(f) &= \tilde{h}(f) \int \ud t \, F(t) e^{-2i\pi f d(t)} \delta(t + d(t) - t_{f}) \nn \\
	&= \tilde{h}(f) F(t_{f}^{d}) \frac{e^{-2i\pi f d(t_{f}^{d})}}{1+\dot{d}(t_{f}^{d})}
\end{align}
In the case of the delay associated with the motion of the constellation around the Sun, the delay takes here a simple form (restoring factors $c$),
\be
	d(t) = \frac{R}{c} \cos(\beta) \cos(\Omega_{0} t -\lambda) \,,
\ee
with $R/c \simeq 500 \mathrm{s}$ and $\Omega_{0}R/c \simeq []$. In the case of the delays between spacecrafts of the constellation, the delays have a more complicated time dependence and scale instead as $L/c \simeq [] \mathrm{s}$ and $\Omega_{0} L/c \simeq []$.

Since the propagation delays are small compared to the characteristic timescale of the orbital motion $T_{0} = 1\mathrm{yr}$, we will be able to treat $d$ as a perturbation in the equations above~\eqref{}. By doing so, we obtain for the delayed time at first order
\begin{align}
	t_{f}^{d} &= t_{f} - d(t_{f}) ( 1 - \dot{d}(t_{f})) + \calO(\Omega_{0}d) \,, \nn\\
	d(t_{f}^{d}) &= d(t_{f}) ( 1 - \dot{d}(t_{f})) + \calO(\Omega_{0}d) \,.
\end{align}
Now, since $\dot{d} \ll 1$, we can consider that the only relevant correction in~\eqref{} comes from the phase factor, where the factor $2\pi f d$ gives an additional magnification by a factor $3.10^{3}$. We thus arrive in this case at the approximate form
\be
	\tilde{s}(f) \simeq \tilde{h}(f) F(t_{f})\exp\left[ -2i\pi f d(t_{f}) (1-\dot{d}(t_{f})) \right] \,.
\ee
